Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
update KMeans++ description

For ASC, the systems are again evaluated on the private part of DCASE2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE2013 dataset, also using five-fold stratified cross validation. Clustering is done using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. \ja{How are they selected differently?}

>>>>

For ASC, the systems are again evaluated on the private part of DCASE2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE2013 dataset, also using five-fold stratified cross validation. Clustering is done using KMeans$++$ \cite{arthur2007k}, an augmented version of K-means with a robust initialization procedure.
